Incentivizing Exploration with Unbiased History

### 2018-10-31 model.tex
Rewrote the model section.

%!TEX root = main.tex
\section{Model}
\label{sec:model}

We study the mult-armed bandit problem in a social learning context, in which a principal faces a sequence of $T$ myopic agents. There is a set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is distributed according to the Bernoulli distribution $\cD_a$ with an unknown mean $\mu_a$. At each round $t\in [T]$, a new agent $t$ arrives, receives a message $m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a reward $r_t\in \{0,1\}$ that is immediately observed by the principal. Given any sequence of arms $\{a_1, \ldots, a_T\}$ chosen by the agents, the \emph{regret} is defined as
\[
  \reg(T)= \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a -
  \sum_{t=1}^T \mu_{a_t}.
\]

\xhdr{Unbiased sub-history policy.} The principal's goal is to reveal a sequence of messages according to a disclosure policy so that the regret of the induced sequence of actions is minimized. We will focus on \emph{unbiased sub-history policies} that at each round $t$ reveal the \emph{sub-history} $H_t = \{(s, a_s, r_s)\mid s \in S_t\}$, such that each $S_t\subseteq [t-1]$ is a subset of previous rounds \emph{fixed ahead of time}. A simple example is the policy that reveals the \emph{full history} with $S_t = [t-1]$.  All of the policies we develop are \emph{transitive}: for any two agents $t$ and $t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains that of $S_{t'}$.

\xhdr{Information flow graph.} We will describe our transitive policies using a \emph{information flow graph} (and henceforth \emph{information graph})---a directed graph over the $T$ agents such that if there is an edge from $u$ to $v$, it means $u\in S_v$. By the property of transitivity, $S_t$ is the set of nodes that can reach node $t$ in the info graph. \niedit{For example, an information graph for the policy that reveals the full history is the directed line graph containing edges $(t,t+1)$ for all $t\in[T-1]$.}

\iffalse
\begin{itemize}
\item \textbf{Full history:} We show each agent the history of all previous agents' pulls. We call this policy \ALGG. 
\item \textbf{Unbiased sub-history:} We show each agent only a subset of history. The subsets are pre-determined before any arms are pulled.  
\item \textbf{Info graph:} All the recommendation policies in this paper can be described by an undirected transitive graph with $T$ nodes. We call it the info graph. The $T$ nodes in the graph represent the $T$ agents. If there is an edge between node $u$ and $v$ for $u < v$, it means the history of agent $u$ is shown to agent $v$.
\end{itemize}
\fi

\begin{remark}
  Why not arbitrary sub-history? \swcomment{important point to make;
    but should be in the introduction}
\end{remark}

\xhdr{Agents' behavior.} \nicomment{re-ordered this.} An {\em agent estimator} is a function that maps the revealed sub-history $H_t$ to a mean reward estimate $\hat{\mu}_a^t$ for every arm $a$. For any $t\in[T]$ and $a\in \A$, we write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls of $a$ and the empirical mean reward of arm $a$ in sub-history $H_t$ respectively. If an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.  We require the following assumptions.

\begin{assumption}
	\label{ass:embehave}
	The set of mean rewards $\{\mu_a\}$, the estimates $\hat \mu_a^t$, and the empirical mean rewards $\bar\mu_a^t$  satisfy:

	\begin{itemize}
		\item The mean reward $\mu_a$ for each arm $a\in \A$ lies in the range
		of $[1/3, 2/3]$.

		\item Let $c_m = 1/16$.\swcomment{maybe use a better notation} \nicomment{yeah, why the subscript $m$? and $T$ below? how about just $\alpha,\beta$ for the constants in this assumption? or $\alpha$ and $N_0$? or use $n_{t,a}$ for number of pulls and $N$ for a constant that you want the $n_{t,a}$ to exceed?}
		% \jmcomment{It means a constant for some assumptions about means but nothing else. Just want to make it different from other constants. Maybe there are better notations.}. 
		There exists a constant $c_T$ such that for any agent $t$ and
		arm $a$, as long as \niedit{$N_{t,a} \geq c_T$}, 
		\[
		\left|\hat{\mu}^t_a - \bar{\mu}^t_a \right| <
		\frac{c_m}{\sqrt{N_{t,a}}}.
		\]
		\item If $N_{t,a} = 0$, the initial estimate
		$\hat{\mu}^t_a$ is at least $1/3$.
	\end{itemize}
\end{assumption}

The first assumption ensures that the reward distributions have sufficient entropy to induce natural exploration. We choose the bounded range $[1/3, 2/3]$ for the simplicity of our analysis, and it can further relaxed to $[1/C, (C-1)/C]$ for any constant $C$. The second assumption says that the estimates computed by the agents are well-behaved, and are close to the empirical estimates given by the sub-history, provided that the number of observations is sufficiently large.

@@

\begin{remark}
We emphasize that the agents we consider in this paper are {\em frequentists}.  Thus their estimators, which determine their behavior, take samples as inputs and not priors.  The estimators satisfying Assumption~\ref{ass:embehave} include that of the natural greedy frequentist, who always pulls the arm with the highest empirical mean.
\end{remark}

Given any bandit instance, we define the \emph{gap parameter} $\Delta$ as the difference between the largest and second largest mean rewards. In general, the gap parameter is unknown to the principal (or the algorithm), but we show how to obtain different forms of regret bounds if $\Delta$ is known.

>>>>

%!TEX root = main.tex
\section{Model and Preliminaries}
\label{sec:model}

\newcommand{\SubH}[1]{H_{#1}} % subhistory
\newcommand{\AnonSubH}[1]{H^{\texttt{anon}}_{#1}} % subhistory

We study the multi-armed bandit problem in a social learning context, in which a principal faces a sequence of $T$ myopic agents. There is a set $\A$ of $K$ possible actions, a.k.a. \emph{arms}. At each round $t\in [T]$, a new agent $t$ arrives, receives a message $m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a reward $r_t\in \{0,1\}$ that is immediately observed by the principal. The reward from pulling an arm $a\in \A$ is drawn independently from Bernoulli distribution $\cD_a$ with an unknown mean $\mu_a$. An agent does not observe anything from the previous rounds, other than the message $m_t$. The problem instance is defined by (known) parameters $K,T$ and the (unknown) tuple of mean rewards, $(\mu_a:\,a\in\A)$. We are interested in \emph{regret}, defined as
\[\textstyle 
  \reg(T)
  %= \reg(a_1, \ldots , a_T) 
  = T \max_{a\in \A} \mu_a -
  \sum_{t\in [T]} \E[\mu_{a_t}].
\]
The principal chooses messages $m_t$ according to an online algorithm called \emph{disclosure policy}, with a goal to minimize regret. We assume that mean rewards are bounded away from $0$ and $1$, to ensure sufficient entropy in rewards. For concreteness, we posit that
    $\mu_a\in [\tfrac13,\tfrac23]$.

\xhdr{Unbiased subhistories.}  
The \emph{subhistory} for a subset of rounds $S\subset [T]$, and the corresponding \emph{anonymized subhistory} are defined, respectively, as
\[ \SubH{S} = \{\; (s,a_s,r_s):\;s\in S \;\}
\quad\text{and}\quad
   \AnonSubH{S} = \{\; (a_s,r_s):\;s\in S \}.
\]
Accordingly, $\SubH{[t-1]}$ is called the \emph{full history} at time $t$.

We focus on disclosure policies of a particular form, where the message in each round $t$ is $m_t = \SubH{S_t}$ for some subset $S_t\subset [t-1]$. We assume that the subset $S_t$ is chosen ahead of time, before round $1$ (and therefore does not depend on the observations $\SubH{t-1}$). Such message is called \emph{unbiased subhistory}, and the resulting disclosure policy is called an \emph{unbiased-history policy}.

Further, we assume that disclosure policies are \emph{transitive}, in the following sense:
\[ t'\in S_t \Rightarrow S_{t'}\subset S_t
    \qquad \text{for all rounds $t,t'\in [T]$}. \]
In words, if agent observes the subhistory for some previous agent, then she observes the entire message for that agent.

A transitive unbiased-history policy $\pi$ can be represented as an undirected graph $G_\pi$, where nodes correspond to rounds, and any two rounds $t'<t$ are connected if and only if $t'\in S_t$ and there is no intermediate round $t''$ with
    $t'\in S_{t''}$ and $t''\in S_t$.
This graph is henceforth called the \emph{information flow graph} of policy $\pi$, or \emph{info-graph} for short.

\xhdr{Agents' behavior.} Let us define agents' behavior in response to an unbiased-history policy. We posit that each agent $t$ uses its observed subhistory $m_t$ to form a reward estimate $\hat{\mu}_{t,a} \in [0,1]$ for each arm $a\in \A$, and chooses an arm with a maximal estimator. (Ties are broken according to an arbitrary rule that is the same for all agents.)
We make some mild assumptions:

%If an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.

\begin{assumption}\label{ass:embehave}
Reward estimates satisfy the following assumptions:
\begin{itemize}
\item[(a)] Reward estimates are close to empirical averages. Let $N_{t,a}$ and $\bar{\mu}_{t,a}$ denote the number of pulls and the empirical mean reward of arm $a$ in subhistory $m_t$. Then for some absolute constant $N_0\in \N$ and $C_0=\tfrac{1}{16}$ it holds that
\[
\forall t\in[T],\, a\in\A \qquad
N_{t,a} \geq N_0 \quad\Rightarrow\quad
    \left|\hat{\mu}^t_a - \bar{\mu}^t_a \right| <
		\frac{C_0}{\sqrt{N_{t,a}}},
\]
\item[(b)] Reward estimates have a warm-start property:
\[
\forall t\in[T],\, a\in\A \qquad
N_{t,a} =0 \quad\Rightarrow\quad
    \hat{\mu}^t_a \geq \tfrac13.
\]

\item[(c)] Reward estimates $\hat{\mu}_a^t$ depend only on the anonymized subhistory $\AnonSubH{S_t}$. That is, reward estimates depend only on the observations, not on the rounds in which these observations are collected.

\item[(c)] Reward estimates are consistent over time, but allow some agent heterogeneity. Formally, each agent $t$ forms its estimates according to a \emph{reward estimate function}: a function $f_t$ from anonymous subhistories to $[0,1]^K$, so that the estimate vector
        $(\hat{\mu}_{t,a}:\, a\in\A)$
    equals $f_t(\AnonSubH{S_t})$. And this function is drawn independently from some fixed distribution over reward estimate functions.
\end{itemize}
\end{assumption}

\OMIT{ %%%%%%%%%%
The first assumption ensures that the reward distributions have sufficient entropy to induce natural exploration. We choose the bounded range $[1/3, 2/3]$ for the simplicity of our analysis, and it can further relaxed to $[1/C, (C-1)/C]$ for any constant $C$. The second assumption says that the estimates computed by the agents are well-behaved, and are close to the empirical estimates given by the sub-history, provided that the number of observations is sufficiently large.

@@

\begin{remark}
We emphasize that the agents we consider in this paper are {\em frequentists}.  Thus their estimators, which determine their behavior, take samples as inputs and not priors.  The estimators satisfying Assumption~\ref{ass:embehave} include that of the natural greedy frequentist, who always pulls the arm with the highest empirical mean.
\end{remark}
} %%%%%%%

\xhdr{Connection to multi-armed bandits.}
The special case when each message $m_t$ is an arm, and the $t$-th agent always chooses this arm, corresponds to a standard multi-armed bandit problem with IID rewards. Following the literature on bandits, we define the \emph{gap parameter} $\Delta$ as the difference between the largest and second largest mean rewards.%
\footnote{Formally, the second-largest mean reward is 
    $\max_{a\in\A:\mu(a)<\mu^*} \mu(a)$,
where $\mu^* = \max_{a\in\A} \mu(a)$.
}
The gap parameter is not known to the principal (in our problem), or to the algorithm (in the bandit problem). However, it is essential for regret bounds.

\ascomment{We'll need to state/discuss optimal regret bounds somewhere, probably here.}
